% Data analysis


# Packages
Here we load all the packages we ae going to use in the analysis.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(gsheet)
library(cowplot)
library(ggthemes)
library(DescTools)
library(minpack.lm)
library(agricolae)
library(readxl)
library(patchwork)
```


# Probability distributions

Fist step is to assemble the probability distributions for the for variable we are going to use for the simulations

## SBR severity on untreated check.

### Import data

Importing data of soybean rust severity (SBR) on the untreated check

```{r}
sev_data = read.csv("data/sev_data.csv")
head(sev_data)
```

Filtering only values of severity in the check treatment
```{r}
sev_check = sev_data %>% 
  filter(active_ingredient == "check")
head(sev_check)
```

### Empirical distribution

```{r}
sev_check %>% 
  ggplot(aes(severity/100))+
  geom_histogram(bins = 20, color = "black", fill = "gray")
```


### Modeling

Since severity in proportional terms is between zero and one, we fit the empirical distribution into a beta probability distribution. For that we need to find the shape and scale parameters of the beta distribution function.

For that, obtain the empirical cumulative distribution and fit to the beta cumulative distribution.

```{r}
sev = sev_check$severity
Fx= environment(ecdf(sev))$y
x = environment(ecdf(sev))$x/100

summary(nlsLM(Fx ~ pbeta(x, shape1, shape2, log = FALSE) ,
      start = c(shape1 = 1, shape2 = 1),
      control = nls.lm.control(maxiter = 100000)))
```

### Kolmogorov-Smirnov Test
```{r}
ks.test(Fx,pbeta(x, 1.707, 1.266) )
```


```{r}
plot(x,Fx)
curve(pbeta(x, 1.707, 1.266),0,1, add = T)
```


```{r}
plot(Fx,pbeta(x, 1.707, 1.266) )
abline(a=0,b=1)
```


### Visualization
```{r}
sev_dist_plot = sev_check %>% 
  ggplot(aes(severity/100))+
 geom_histogram(aes(y = ..density..),bins = 10, color = "white", fill = "#AC08FF")+
   stat_function(fun=function(x) dbeta(x, 1.707, 1.266), color= "black", size = 1.2)+
  theme_bw()+
  labs(x="Severity (proportion)", y = "Density")
sev_dist_plot
# ggsave("figs/sev_dist.png", dpi=600, height = 3, width = 4)
```



## Soybean price 

### Import data

```{r}
soybean = gsheet2tbl("https://docs.google.com/spreadsheets/d/1-jQ9OgWdLQCb0iB0FqbrhuVi7LiNhqxvf9QU4-iuc3o/edit#gid=1085329359") 
head(soybean)
```


conversion to US dollar
```{r}
sbr_price = soybean %>% 
  filter(year>=2018) %>% 
  mutate(price = (price/60)/4,
         national_price = (national_price/60)/4)
sbr_price
```

```{r}
sbr_price %>% 
  ggplot(aes(year,price)) +
  geom_jitter(alpha =.2, size =2)+
  geom_boxplot(aes(group = year), fill = NA, size= 1)+
  scale_color_gradient()+
  theme_minimal_hgrid()
  # facet_wrap(~state)
```


Mean and Standad deviantion

```{r}
mean(sbr_price$price)
sd(sbr_price$price)
```

### Empirical distribution

```{r}
sbr_price %>% 
  ggplot(aes(price))+
  geom_histogram(bins = 10, fill = "steelblue", color = "white")+
  theme_bw()+
  labs(x = "Soybean prince")+
  scale_x_continuous(breaks = seq(0,1,by=0.025))
```


 
```{r}
hist((sbr_price$price), prob = T)
curve(dnorm(x, mean(sbr_price$price), sd(sbr_price$price)),0.15,0.35, add = T)
```


```{r}
plot(ecdf(sbr_price$price))
curve(pnorm(x, mean(sbr_price$price), sd(sbr_price$price)),0.2,0.35, add = T)
```

Mean and median
```{r}
mean(sbr_price$price)
median(sbr_price$price)
```

### Shapiro
```{r}
shapiro.test(sbr_price$price)
```

### Kolmogorov-Smirnov Test
```{r}
Fx = environment(ecdf(sbr_price$price))$y
x= environment(ecdf(sbr_price$price))$x
ks.test(Fx, pnorm(x, mean(sbr_price$price), sd(sbr_price$price)))
```

```{r}
plot(Fx, pnorm(x, mean(sbr_price$price), sd(sbr_price$price)))
```


### Vizualization

```{r}
price_plot = sbr_price %>% 
  ggplot(aes(price))+
 geom_histogram(aes(y = ..density..),bins = 10, color = "white", fill = "#1C8C20")+
   stat_function(fun=function(x) dnorm(x, mean(sbr_price$price), sd(sbr_price$price)), color= "black", size = 1.2)+
  theme_bw()+
  labs(x="Soybean price (US$/kg)", y = "Density")+
  scale_x_continuous(breaks = seq(0,1,by=0.025))
price_plot
# ggsave("figs/sev_dist.png", dpi=600, height = 3, width = 4)
```




## Regression coeficients 

### import data
Importing regression Slope and intercept data from the relationship between SBR severity and yield

```{r}
damage_data = read_excel("data/dados histograma.xlsx") %>% 
  mutate(Slope = b1,
         Intercept = b0) %>% 
  dplyr::select(-b1,-b0)
head(damage_data)
```

### Empirical distribution
Visualizando os hitogramas do slope e intercepto

```{r}
damage_data %>% 
  gather(2:3, key = "par", value = "value") %>% 
  ggplot(aes(value))+
  geom_histogram(bins = 10, color = "gray40", fill = "gray90")+
  facet_wrap(~par, scales = "free_x")+
  theme_bw()
```


### Regression lines
```{r}
  ggplot() +
  geom_point(aes(x = 0:100, y = seq(0,5000,by = 50)), color = NA)+
  geom_abline(data =damage_data, aes(slope = Slope, intercept = Intercept),
              alpha = 0.5, color = "gray")+
  geom_abline(intercept = 2977,slope = -18, size = 1.2)+
  geom_abline(intercept = 2862,slope = -19.4 , size = .51, linetype = 2)+
  geom_abline(intercept = 3093,slope = -16.6, size = .51, linetype = 2)+
  
  labs(x = "SBR Severity (%)", y = "Yield (kg/ha) ")+
  theme_base()
  
```

### correlation
Correlation between slope and intercept

```{r}
correlation(damage_data$Slope, damage_data$Intercept)
```

#### plot 
```{r}
corr_emp_plot = damage_data %>% 
  ggplot(aes(Intercept, Slope))+
  geom_point(color = "black", size =2, alpha =0.5)+
  # geom_density2d_filled()+
  geom_smooth(method = "lm", se = F, color ="Red", size=1.2, fullrange=TRUE)+
  theme_light()+
  labs(title = "Empirical: r = -0.216")+
  coord_cartesian(
    xlim = c(0,6000),
    ylim = c(-75,0)
  )
corr_emp_plot
```


### Cumulative density

### Intercept
```{r}
mean_intercept = mean(damage_data$Intercept)
sd_intercept = sd(damage_data$Intercept)

plot(ecdf(damage_data$Intercept))
curve(pnorm(x, mean_intercept,sd_intercept), 1000,5000, add = T, col = "red")
```

### Kolmogorov-Smirnov Test
```{r}
Fx = environment(ecdf(damage_data$Intercept))$y
x= environment(ecdf(damage_data$Intercept))$x
ks.test(Fx, pnorm(x, mean(damage_data$Intercept), sd(damage_data$Intercept)))
```
```{r}
plot(Fx, pnorm(x, mean(damage_data$Intercept), sd(damage_data$Intercept)))
```



```{r}
intercep_plot = damage_data %>% 
  ggplot(aes(Intercept))+
  geom_histogram(aes(y = ..density..),bins = 10, color = "white", fill = "#FF4917")+
  stat_function(fun=function(x) dnorm(x, mean_intercept, sd_intercept), color ="black", size =1.2)+
  theme_bw()+
  labs(x="Intercept (kg/ha)", y = "Density")
intercep_plot
```





### Slope

```{r}
mean_slope = mean(damage_data$Slope)
sd_slope = sd(damage_data$Slope)

plot(ecdf(damage_data$Slope))
curve(pnorm(x, mean_slope, sd_slope), -60,5, add = T, col = "red")

```


#### Modeling
Fitting gamma distribution to the empirical cumulative density of the slope data
```{r}
Fx =environment(ecdf(-damage_data$Slope))$y
x = environment(ecdf(-damage_data$Slope))$x

slope_reg = nlsLM(Fx ~ pgamma(x, shape, rate,log = FALSE) ,
      start = c(shape = 2.5, rate = 0.13),
      control = nls.lm.control(maxiter = 1024))
summary(slope_reg)

```

### Kolmogorov-Smirnov Test
```{r}
shape = summary(slope_reg)$coef[1]
rate = summary(slope_reg)$coef[2]

Fx =environment(ecdf(-damage_data$Slope))$y
x = environment(ecdf(-damage_data$Slope))$x
ks.test(Fx, pgamma(x, shape, rate))
```


```{r}
shape = summary(slope_reg)$coef[1]
rate = summary(slope_reg)$coef[2]

slope_plot = damage_data %>% 
  ggplot(aes(Slope))+
 geom_histogram(aes(y = ..density..),bins = 10, color = "white", fill = "#159EE6")+
   stat_function(fun=function(x) dgamma(-x, shape, rate), size = 1.2, color = "black")+
  theme_bw()+
  labs(x="Slope (kg/p.p.)", y = "Density")
slope_plot
```

### Kolmogorov-Smirnov Test
```{r}

ks.test(Fx,pgamma(x, shape, rate))

```




### Multivariate Simulation using copula 

Simulating two normal distributions correlated 
#### Function


```{r}
######################################
gera.norm.bid.geral<-function(tamanho.amostra,correlacao,m1,m2,sigma1,sigma2)
{
  ro<-correlacao
  n<-tamanho.amostra
  x<-matrix(0,n,2)
  for (i in 1:n)
  {x[i,1]<-rnorm(1,m1,sigma1)
  x[i,2]<-rnorm(1,m2+ro*sigma1/sigma2*(x[i,1]-m1),sigma2*(sqrt(1-ro^2)))
  }
  return(x)
}

```

Test for correlation of 0.9
```{r}
#testando
j<-gera.norm.bid.geral(1000,0.9,0,0,1,1)

plot(j[,1],j[,2])
```

For our data, we will use the positive correlation, becouse we want positive values of slope 
```{r}
#testando
j<-gera.norm.bid.geral(10000,0.2160089,0,0,1,1)

plot(j[,1],j[,2])
```



### Intercept
Now we obtaing the probabilities from first distribution and insert in the quantiles function for the normal distribution of the intercept

```{r}
b0 = pnorm(j[,2])
b0_t = qnorm(b0, 2977, 58.9*sqrt(210))
hist(b0_t, prob = T)
curve(dnorm(x, mean_intercept, sd_intercept), 0, 6000, add = T)
```


### Slope
Now we obtaing the probabilities from first distribution and insert in the quantiles function for the gamma ditribution and multiply for -1 for obtain the negative outputs of the coeficient 
```{r}
b1 = pnorm(j[,1])
b1_t = qgamma(b1, shape, rate = rate)*-1
hist(b1_t, prob = T)
curve(dgamma(-x,shape=shape, rate = rate), -60,0, add = T)
```


Now we recalculate the correlation between the simulated coeficients. It matchs!

```{r}
correlation(b1_t, b0_t)
```


#### Viz. the correlation
```{r}
corr_sim_plot = data.frame(b0_t,b1_t ) %>%
  mutate(alfa =(b1_t/b0_t)*100 ) %>% 
  filter(alfa > -3 & alfa < 0) %>% 
ggplot(aes(b0_t,b1_t ))+
  geom_point( size =2, color = "orange", alpha =0.3)+
  # geom_density_2d(color = "black")+
  geom_smooth(method = lm, color = "red", se = F, size = 1.2)+
  theme_light()+
  labs(y= "Slope",
       x = "Intercept",
       title = "Simulated: r = -0.204")+
  coord_cartesian(
    xlim = c(0,6000),
    ylim = c(-75,0)
  )
corr_sim_plot
```


#### Combo distributions

```{r}

# plot_grid(sev_dist_plot,price_plot, intercep_plot, slope_plot, labels = "AUTO", nrow =2)

(sev_dist_plot+price_plot)/
  (intercep_plot+slope_plot)+
  # (corr_emp_plot+corr_sim_plot)+
  plot_annotation(tag_levels = 'A')&
  theme(plot.title = element_text(size =8))
  
ggsave("figs/coef_dist.png", dpi = 600, height = 5, width = 6)
ggsave("figs/coef_dist.pdf", dpi = 600, height = 5, width = 6)
```



### Relative yield loss

Here we calculate the yield relative loss due to SBR severity using the original data set

```{r}
empiric_ryl= damage_data %>% 
  mutate(cc = (Slope/Intercept)*100) %>% 
  filter( cc > -3 & cc <0 )
head(empiric_ryl)
```

```{r}
stat_emp_ryl =empiric_ryl%>% 
  summarise(data = "empirical",
            mean =  mean(cc),
            median =  median(cc),
            variance = var(cc))
```


```{r}

real_RYL= empiric_ryl %>% 
  ggplot(aes(cc))+
 geom_histogram(aes(y = ..density..),bins = 10, color = "white", fill = "black")+
  scale_y_continuous(limits = c(0,1.4),breaks =  seq(0, 1.4,by = 0.4))+
  geom_vline(data = stat_emp_ryl, aes(xintercept = mean, color = "Mean"),size =1)+
  geom_vline(data = stat_emp_ryl, aes(xintercept = median, color = "Median"),size =1)+
  theme_bw()+
  scale_color_calc()+
  labs(x = "Relative yield loss (%/p.p.)",
       y = "Density",
       color = "",
       title = "Empirical")+
  xlim(-3,0.2)+
  theme(legend.position = "top")
real_RYL
```

And here we calculate the relative yield loss due to SBR severity using the simulated data set


```{r}
simul_ryl = data.frame(b0_t, b1_t, cc = (b1_t/b0_t)*100) %>% 
  filter( cc > -3 & cc <0 )
head(simul_ryl)
```

```{r}
stat_suml_ryl = simul_ryl%>% 
  summarise(data = "Simulated",
            mean =  mean(cc),
            median =  median(cc),
            variance = var(cc))
```


```{r}
simul_RYL =simul_ryl %>% 
  ggplot(aes(cc))+
 geom_histogram(aes(y = ..density..),bins = 10, color = "white", fill = "orange")+
  scale_y_continuous(limits = c(0,1.4),breaks =  seq(0, 1.4,by = 0.4))+
  geom_vline(data = stat_suml_ryl, aes(xintercept = mean, color = "Mean"),size =1)+
  geom_vline(data = stat_suml_ryl, aes(xintercept = median, color = "Median"),size =1)+
  theme_bw()+
  scale_color_calc()+
  labs(x = "Relative yield loss (%/p.p.)",
       y = "Density",
       color ="",
       title = "Simulated")+
  xlim(-3,0.2)+
  theme(legend.position = "top")
simul_RYL

```

### Comparision of mean, median and variance 

```{r}
damage_data %>% 
  mutate(cc = (Slope/Intercept)*100) %>% 
  filter( cc > -3 & cc <0 ) %>% 
  summarise(data = "empirical",
            mean =  mean(cc),
            median =  median(cc),
            variance = var(cc)) %>% 
  bind_rows(
    data.frame(b0_t, b1_t, cc = (b1_t/b0_t)*100) %>% 
  filter( cc > -3 & cc <0 ) %>% 
  summarise(data = "Simulated",
            mean =  mean(cc),
            median =  median(cc),
            variance = var(cc))
  )

```


### Kolmogorov-Smirnov Test
```{r}
actual_cc = damage_data %>% 
  mutate(cc = (Slope/Intercept)*100)

simulated_cc = data.frame(b0_t, b1_t, cc = (b1_t/b0_t)*100) %>% 
  filter( cc > -3 & cc <0 )
```

Distribution
```{r}
ks.test(actual_cc$cc, simulated_cc$cc)
```

cummulative distribution
```{r}
fx_actual = environment(ecdf(actual_cc$cc))$y
fx_simu = environment(ecdf(simulated_cc$cc))$y
ks.test((fx_actual),(fx_simu))
```

```{r}
ecdf_damage = ggplot()+
  stat_ecdf(aes(simulated_cc$cc,color = "Simulated"), size=1.2,geom = "step")+
  stat_ecdf(aes(actual_cc$cc, color = "Empirical"), size=1.2,geom = "step")+
  theme_bw()+
  scale_color_manual(values = c("black","orange"))+
  labs(y = "Probability",
       x = "Relative percent yield loss",
       color ="",
       title = "Cumulative distribution function")+
  theme(legend.position = "top",
        legend.background = element_blank())
ecdf_damage
```


### Combo Yield loss

```{r fig.height=3, fig.width=8}
((corr_emp_plot/corr_sim_plot)|(real_RYL/simul_RYL)+plot_layout(guides = 'collect')| ecdf_damage ) +
  # plot_layout(heights = c(1,1,0.5))+
  plot_annotation(tag_levels = 'A') & 
  
  theme(legend.position = 'bottom',
        plot.title = element_text(size=9),
        legend.key.size= unit(3, "mm"),
        legend.text =  element_text(size = 7))

ggsave("figs/RYL.png", dpi = 600, height = 5, width = 10)
ggsave("figs/RYL.pdf", dpi = 600, height = 5, width = 10)
```


# Simulations 
```{r}
set.seed(1)
n=40000
lambda = seq(0,1, by=0.05)
fun_price = seq(-10, 260, by=15)
n_aplication = 1
operational_cost = 10  

comb_matrix = as.matrix(data.table::CJ(lambda,fun_price))
colnames(comb_matrix) = c("lambda","fun_price")
comb_matrix = cbind(comb_matrix,operational_cost, n_aplication)
C = comb_matrix[,"n_aplication"]*(comb_matrix[,"operational_cost"]+comb_matrix[,"fun_price"] )
comb_matrix = cbind(comb_matrix,C)

N = length(comb_matrix[,1])*n
big_one = matrix(0, ncol = 12, nrow =N)
big_one[,1] = rep(comb_matrix[,1],n)
big_one[,2] = rep(comb_matrix[,2],n)
big_one[,3] = rep(comb_matrix[,3],n)
big_one[,4] = rep(comb_matrix[,4],n)
big_one[,5] = rep(comb_matrix[,5],n)

set.seed(1)
sn = rbeta(N, 1.707, 1.266)
sf = sn*(1-big_one[,1])
# simulating the coeficientes 
set.seed(1)
normal_correlated<-gera.norm.bid.geral(N,0.21,0,0,1,1)
b0_n = pnorm(normal_correlated[,2])
b1_n = pnorm(normal_correlated[,1])
b0 = qnorm(b0_n, mean_intercept,sd_intercept)
b1 = -qgamma(b1_n, shape, rate,)
rm(b0_n,b1_n,normal_correlated)
# b0[b0<0] = 0.0001
# Calculating the alha coeficient
alfa = (b1/b0)*100
# alfa[alfa > 0] = 0
# alfa[alfa < -3] = -3

# Calculating yield gain
# yn = b0*(1+sn*alfa) # Yield  non-treated
# yf = b0*(1+sf*alfa) # Yield  treated
yn  = b0 - (-alfa*b0*sn)
yf  = b0 - (-alfa*b0*sf)
# yn[yn<0] = 0
# yf[yf<0] = 0
# yield_gain = yf-yn # yield gain
# yield_gain_perc = (1-(yn/yf))*100


# Simulating soybean price
set.seed(1)
soy_price = rnorm(N, mean(sbr_price$price),sd(sbr_price$price))
# income = yield_gain*soy_price # calculating the income

big_one[,6] = yn
big_one[,7] = yf
big_one[,8] = soy_price
big_one[,9] = b1
big_one[,10] = alfa
big_one[,11] = b0
big_one[,12] = sn
colnames(big_one)  = c("lambda","fun_price","operational_cost","n_aplication","C","yn","yf","soy_price","b1","alfa","b0", "sn")
```


```{r}
big_one_df = as.data.frame(big_one) %>% 
  filter(b0>=0) %>% 
  filter(yn>0) %>% 
  filter(alfa > -3 & alfa < 0) %>% 
  mutate(yield_gain = yf-yn,
         # yield_gain_perc = ((yf - yn)/yn)*100,
         yield_gain_perc = ((yf/yn)-1)*100,
         income = yield_gain*soy_price,
         CP = C/soy_price,
         # profit = (yield_gain>=CP)*1,
         profit = (income>=C)*1)
  

```


### Breacking even

#### Tetris

```{r}
big_one_df %>% 
  # mutate(sev_class = case_when(sn > median(sn) ~ "High severity",
                                 # sn <= median(sn) ~ "Low severity")) %>% 
  filter(lambda >=0.3) %>%
  group_by(lambda, C) %>% 
  summarise(n=n(),sumn = sum(profit), prob = sumn/n) %>%
  # filter(prob>0.5) %>%
  mutate(prob2 = case_when(prob < 0.50 ~ "Pr(I \u2265 C) \u2264 0.5 ",
                          prob >= 0.50 ~ "Pr(I \u2265 C) > 0.5")) %>% #,
  # #                         prob >= 0.75 ~ "75% \u2264 p < 100% "  )) %>% 
  ggplot(aes(as.factor(lambda*100),as.factor(C), fill = prob, 
             # color = prob2
             ))+
  geom_tile(size = 0.5, color ="white")+
  scale_fill_viridis_b(option ="B", direction = -1)+
  # scale_fill_manual(values = c("darkred",  "steelblue"))+
  # scale_fill_gradient2(low = "#E60E00",mid = "#00030F", high = "#55E344",midpoint = 0.5)+
  scale_color_manual(values = c("#E60E00","#55E344"))+
  # scale_fill_gradient2(low = "red",mid = "black", high = "steelblue",midpoint = 0.5)+
  # scale_color_manual(values = c("red","steelblue")) + 
  guides(color = guide_legend(override.aes = list(size=2)))+
  # scale_fill_viridis_d(option = "B")+
  labs(x = "Fungicide efficacy (%)",
       y = "Fungicide + Application cost ($)",
       fill  = "Pr(I \u2265 C)",
       color ="" )+
  # facet_wrap(~sev_class)+
  theme_light()
# ggsave("figs/tetris.png", dpi = 600, height = 5, width = 7)
```

#### Tetris 2

```{r}
median(big_one_df$b0)
```

```{r}
tetris_plot = function(s_class, y_class, pal =1){
big_one_df %>% 
  mutate(sev_class = case_when(sn > median(sn) ~ "High severity",
                                 sn <= median(sn) ~ "Low severity"),
      yield_class =  case_when(b0 > median(b0) ~ "High yield",
                                 b0 <= median(b0) ~ "Low yield")) %>%
    filter(lambda >=0.3) %>% 
  group_by(lambda, C, sev_class,yield_class) %>% 
  summarise(n=n(),sumn = sum(profit), prob = sumn/n) %>%
  mutate(prob = case_when(prob >= .75 ~ "\u2265 0.75",
                          prob < .75 & prob >= 0.5 ~ "0.50-0.75",
                          prob < .50 & prob >= .25 ~ "0.25-0.50",
                          prob < .25 ~ "< 0.25"),
         prob =factor(prob,level = c("< 0.25","0.25-0.50","0.50-0.75", "\u2265 0.75"))) %>%
    filter(sev_class== s_class,
           yield_class == y_class) %>% 
  ggplot(aes(as.factor(lambda*100),as.factor(C), fill = prob))+
  geom_tile(size = 0.25, color ="gray70")+
  scale_fill_brewer(palette = pal)+
  labs(x = "Fungicide efficacy (%)",
       y = "Fungicide + Application cost ($)",
       fill  = "Probability",
       color ="" )+
  # facet_grid(~sev_class)+
  guides(color = guide_legend(override.aes = list(size=2)))+
  theme_light()+
  theme(text = element_text(size = 10),
        legend.position = "bottom",
        axis.text = element_text(size = 7),
        panel.spacing = unit(1.75, "lines"),
        strip.background =element_rect(fill="NA"),
        strip.text = element_text(color = "black", size =12))
}

```

```{r}
tetris_Sh_Sh = tetris_plot(s_class = "High severity",
                          y_class = "High yield",pal =1)+
  labs(title = "High severity",
       subtitle = "High yield")

tetris_Sl_Yh = tetris_plot(s_class = "Low severity",
                          y_class = "High yield",pal =1
                         )+
  labs(title = "Low severity",
       subtitle = "High yield")

tetris_Sh_Yl = tetris_plot(s_class = "High severity",
                          y_class = "Low yield",pal =2
                         )+
  labs(title = "High severity",
       subtitle = "Low yield")

tetris_Sl_Sh = tetris_plot(s_class = "Low severity",
                          y_class = "Low yield",pal =2
                         )+
  labs(title = "Low severity",
       subtitle = "Low yield")


```



#### Combo tetris
```{r}
((tetris_Sh_Sh+tetris_Sl_Yh)+plot_layout(guides = "collect"))/((tetris_Sh_Yl+tetris_Sl_Sh)+
   plot_layout(guides = "collect"))+
  plot_annotation(tag_levels = 'A')&
  theme(legend.position = "bottom",
        plot.title = element_text(size = 8),
        plot.subtitle = element_text(size = 8))
  

ggsave("figs/box_classes.png", dpi = 500, height = 8.5, width = 7.5)
ggsave("figs/box_classes.pdf", dpi = 500, height = 8.5, width = 7.5)
```



## Yield gain
### Absolute gain

```{r}
overal_yg = big_one_df %>%
  mutate(sev_class = " Overall") %>% 
  group_by(lambda,sev_class) %>% 
  summarise(yield_gain_median = median(yield_gain),
            yield_gain_mean = mean(yield_gain),
            up_95 = quantile(yield_gain, 0.975),
            low_95 = quantile(yield_gain, 0.025),
            up_75 = quantile(yield_gain, 0.75),
            low_75 = quantile(yield_gain, 0.25))
```

```{r}
# m_absol = lm(yield_gain ~ lambda, big_one_df %>% mutate(lambda=lambda*100))
# summary(m_absol)
```




```{r}
over_gg_kg = overal_yg %>% 
  ggplot(aes(lambda*100,yield_gain_mean))+
  geom_line(aes(lambda*100, low_95),
              linetype = 2,
            size = 0.7,
            fill = NA)+
  geom_line(aes(lambda*100, up_95),
              linetype = 2,
            size = 0.7,
            fill = NA)+
  geom_line(size = 1.2, aes(lambda*100,yield_gain_median))+
  # scale_linetype_manual(values=c(1,2))+
  theme_light()+
  # geom_abline(slope = 9.61, intercept = -0.1 )+
  # coord_equal()+
  labs(x = "Fungicide efficacy (%)",
       y = "Yield gain (kg/ha)",
       color = "Fungicide mixture", #(Dalla lana et al., 2018)
       linetype = "", fill = "")
over_gg_kg
```




```{r}
ygain_plot = function(s_class){
big_one_df %>% 
  mutate(sev_class = case_when(sn > median(sn) ~ "High severity",
                                 sn <= median(sn) ~ "Low severity"),
      yield_class =  case_when(b0 > median(b0) ~ "High yield",
                                 b0 <= median(b0) ~ "Low yield")) %>%
  group_by(lambda, sev_class,yield_class ) %>% 
  summarise(yield_gain_median = median(yield_gain),
            yield_gain_mean = mean(yield_gain),
            up_95 = quantile(yield_gain, 0.975),
            low_95 = quantile(yield_gain, 0.025),
            up_75 = quantile(yield_gain, 0.75),
            low_75 = quantile(yield_gain, 0.25)) %>% 
  mutate(sev_class = factor(sev_class, levels = c("Low severity","High severity"))) %>%
    filter(sev_class ==s_class ) %>% 
  ggplot(aes(lambda*100,yield_gain_mean))+
  geom_line(aes(lambda*100, low_95, color = yield_class),
              linetype = 2,
            size = 0.7,
            fill = NA)+
  geom_line(aes(lambda*100, up_95,color = yield_class),
              linetype = 2,
            size = 0.7,
            fill = NA)+
  geom_line(size = 1.2, aes(lambda*100,yield_gain_median,color = yield_class))+
  # scale_color_manual(values = c("#009628","#8A0004"))+
  scale_color_manual(values = c("steelblue","#009628"))+
  theme_light()+
    coord_cartesian(ylim=c(0,3000))+
  labs(x = "Fungicide efficacy (%)",
       y = "Yield gain (kg/ha)",
       color = "Attainable Yield", #(Dalla lana et al., 2018)
       linetype = "")
}
high_sev_yg = ygain_plot(s_class = "High severity")+
  labs(title = "High severity")
low_sev_yg = ygain_plot(s_class = "Low severity")+
  labs(title = "Low severity")
```


```{r}
high_sev_yg+low_sev_yg
```

```{r}
big_one_df %>%
  mutate(sev_class = case_when(sn > median(sn) ~ "High severity",
                                 sn <= median(sn) ~ "Low severity"),
      yield_class =  case_when(b0 > median(b0) ~ "High yield",
                                 b0 <= median(b0) ~ "Low yield")) %>%
  group_by(lambda, sev_class,yield_class ) %>% 
  summarise(yield_gain_mean = mean(yield_gain),
            yield_gain_median = median(yield_gain, na.rm = T),
            low_95 = quantile(yield_gain, 0.025),
            up_95 = quantile(yield_gain, 0.975),
            up_75 = quantile(yield_gain, 0.75),
            low_75 = quantile(yield_gain, 0.25)) %>% 
  bind_rows(overal_yg) %>% 
  filter(lambda==.75) %>% 
  arrange(yield_class)


```


### Percent  gain 

```{r}
overal_percet = big_one_df %>%
  mutate(sev_class = " Overall") %>% 
  group_by(lambda,sev_class) %>% 
  mutate(yield_gain_perc = case_when(yield_gain_perc>quantile(yield_gain_perc,0.999)~quantile(yield_gain_perc,0.999),
                                     yield_gain_perc<=quantile(yield_gain_perc,0.999) ~yield_gain_perc)) %>%
  summarise(yield_gain_mean = mean(yield_gain_perc,na.rm = T),
            yield_gain_median = median(yield_gain_perc,na.rm = T),
            low_95 = quantile(yield_gain_perc, 0.025,na.rm = T),
            up_95 = quantile(yield_gain_perc, 0.975,na.rm = T),
            up_75 = quantile(yield_gain_perc, 0.75,na.rm = T),
            low_75 = quantile(yield_gain_perc, 0.25,na.rm = T))  



```


```{r}
over_gg = overal_percet %>% 
  ggplot(aes(lambda*100,yield_gain_mean))+
  geom_line(aes(lambda*100, low_95),
              linetype = 2,
            size = 0.7,
            fill = NA)+
  geom_line(aes(lambda*100, up_95),
              linetype = 2,
            size = 0.7,
            fill = NA)+
  geom_line(size = 1.2, aes(lambda*100,yield_gain_median))+
  # scale_linetype_manual(values=c(1,2))+
  theme_light()+
  # coord_equal()+
  labs(x = "Fungicide efficacy (%)",
       y = "Yield gain %",
       color = "Fungicide mixture", #(Dalla lana et al., 2018)
       linetype = "", fill = "")+
  coord_cartesian(ylim = c(0,100), xlim = c(-10,100))
over_gg
```



```{r fig.height=5, fig.width=12}
ygain_perc_plot = function(s_class){
big_one_df %>% 
  mutate(sev_class = case_when(sn > median(sn) ~ "High severity",
                                 sn <= median(sn) ~ "Low severity"),
      yield_class =  case_when(b0 > median(b0) ~ "High yield",
                                 b0 <= median(b0) ~ "Low yield")) %>%
  group_by(lambda, sev_class,yield_class ) %>% 
  summarise(yield_gain_median = median(yield_gain_perc),
            yield_gain_mean = mean(yield_gain_perc),
            up_95 = quantile(yield_gain_perc, 0.975),
            low_95 = quantile(yield_gain_perc, 0.025),
            up_75 = quantile(yield_gain_perc, 0.75),
            low_75 = quantile(yield_gain_perc, 0.25)) %>% 
  mutate(sev_class = factor(sev_class, levels = c("Low severity","High severity"))) %>%
    filter(sev_class ==s_class ) %>% 
  ggplot(aes(lambda*100,yield_gain_mean))+
  geom_line(aes(lambda*100, low_95, color = yield_class),
              linetype = 2,
            size = 0.7,
            fill = NA)+
  geom_line(aes(lambda*100, up_95,color = yield_class),
              linetype = 2,
            size = 0.7,
            fill = NA)+
  geom_line(size = 1.2, aes(lambda*100,yield_gain_median,color = yield_class))+
  # scale_color_manual(values = c("#009628","#8A0004"))+
  scale_color_manual(values = c("steelblue","#009628"))+

  theme_light()+
  labs(x = "Fungicide efficacy (%)",
       y = "Yield gain (%)",
       color = "Attainable Yield", 
       linetype = "", fill = "")+
  coord_cartesian(ylim = c(0,100))
}
high_sev_yg_perc = ygain_perc_plot(s_class = "High severity")+
  labs(title = "High severity")
low_sev_yg_perc = ygain_perc_plot(s_class = "Low severity")+
  labs(title = "Low severity")

```

### Combo yied gain
```{r}
(high_sev_yg+low_sev_yg)/
(high_sev_yg_perc+low_sev_yg_perc)+
  plot_layout(guides = "collect",
               heights = c(1,1))+
  plot_annotation(tag_levels = 'A')& 
  theme(plot.title = element_text(size =8))
  
  
ggsave("figs/yield_gain_perc.png", dpi = 600, height = 6, width =8)
ggsave("figs/yield_gain_perc.pdf", dpi = 600, height = 6, width =8)
```



```{r}
 big_one_df %>%
  mutate(sev_class = case_when(sn > median(sn) ~ "High severity",
                                 sn <= median(sn) ~ "Low severity"),
      yield_class =  case_when(b0 > median(b0) ~ "High yield",
                                 b0 <= median(b0) ~ "Low yield")) %>%
  group_by(lambda,sev_class,yield_class) %>%
  mutate(yield_gain_perc = case_when(yield_gain_perc>quantile(yield_gain_perc,0.999)~quantile(yield_gain_perc,0.999),
                                     yield_gain_perc<=quantile(yield_gain_perc,0.999) ~yield_gain_perc)) %>%
  summarise(yield_gain_mean = mean((yield_gain_perc),na.rm = T),
            yield_gain_median = median((yield_gain_perc),na.rm = T),
            low_95 = quantile((yield_gain_perc), 0.025,na.rm = T),
            up_95 = quantile((yield_gain_perc), 0.975,na.rm = T),
            up_75 = quantile((yield_gain_perc), 0.75,na.rm = T),
            low_75 = quantile((yield_gain_perc), 0.25,na.rm = T)) %>% 
  bind_rows(overal_percet)%>% 
  filter(lambda==0.75) %>% 
  arrange(yield_class)

```


# Examples

Fungicide PICO+TEBU

```{r}
n = 1000
# yield = rnorm(1000,682.11, 28.97)
efficacy = (1-exp(rnorm(1000,-1.204,0.0462)))

sev_n = rbeta(n, 1.707, 1.266)
sev_f = sev_n*(1-efficacy) 

normal_correlated<-gera.norm.bid.geral(n,0.21,0,0,1,1)
b0_n = pnorm(normal_correlated[,2])
b1_n = pnorm(normal_correlated[,1])
b0 = qnorm(b0_n, mean_intercept,sd_intercept)
b1 = -qgamma(b1_n, shape, rate,)
rm(b0_n,b1_n,normal_correlated)

# Calculating the alpha coeficient
alfa = (b1/b0)*100

# Calculating yield gain
yn  = b0 - (-alfa*b0*sev_n)
yf  = b0 - (-alfa*b0*sev_f)

cost = 125
soy_price = rnorm(n, mean(sbr_price$price),sd(sbr_price$price))

yield_gain = yf-yn
yield_gain_perc = ((yf - yn)/yn)*100
yield_gain_perc = ((yf/yn)-1)*100
income = yield_gain*soy_price
CP = cost/soy_price
profit = (yield_gain>=CP)*1
mean(profit)

hist(income-cost)
hist(efficacy)
```


## simulations overtime
### Tebu
```{r}
box_time = data.frame()
time = seq(0,10, 1)

b0_decline =-1.518
b0_se_decline =  0.065
b1_decline = 0.147
b1_se_decline = 0.012
n = 30000
for(i in 1:length(time)){
  
y =  rnorm(n, b0_decline,b0_se_decline) + time[i]* rnorm(n,b1_decline,b1_se_decline)  
efficacy = (1-exp(y))
a = data.frame(time = time[i],lambda=efficacy)
box_time = box_time %>% 
  bind_rows(a)
}

# box_time



# box_time %>% 
#   ggplot(aes(time, lambda*100))+
#   geom_point()+
#   labs(y = "Efficacy")+
#   ylim(0,100)

```

```{r}
simul_decay = function(data_ef, cost){
# cost = 75
N = n*length(time)
sev_n = rbeta(N, 1.707, 1.266)
sev_f = sev_n*(1-data_ef$lambda) 
normal_correlated<-gera.norm.bid.geral(N,0.21,0,0,1,1)
b0_n = pnorm(normal_correlated[,2])
b1_n = pnorm(normal_correlated[,1])
b0 = qnorm(b0_n, mean_intercept,sd_intercept)
b1 = -qgamma(b1_n, shape, rate,)
rm(b0_n,b1_n,normal_correlated)

# Calculating the alpha coeficient
alfa = (b1/b0)*100

# Calculating yield gain
yn  = b0 - (-alfa*b0*sev_n)
yf  = b0 - (-alfa*b0*sev_f)

soy_price = rnorm(N, mean(sbr_price$price),sd(sbr_price$price))

yield_gain = yf-yn
yield_gain_perc = ((yf - yn)/yn)*100
yield_gain_perc = ((yf/yn)-1)*100
income = yield_gain*soy_price
CP = cost/soy_price
profit = (yield_gain>=CP)
profit_50 = (income>=cost+(cost*0.5))#*1

box_time2 = data_ef %>% 
  mutate(yield_gain) %>% 
  mutate(yield_gain_perc) %>% 
  mutate(income) %>% 
  mutate(CP, cost) %>% 
  mutate(profit,
         profit_50) %>% 
  group_by(time) %>% 
  mutate(P = mean(profit),
         P_50 = mean(profit_50))
return(box_time2)
}

```

```{r}
tebu_75 = simul_decay(data_ef = box_time, cost = 75)
tebu_100 = simul_decay(data_ef = box_time, cost = 100)
tebu_125 = simul_decay(data_ef = box_time, cost = 125)
tebu = bind_rows(tebu_75,tebu_100, tebu_125)
```


```{r}
tebu %>% 
  group_by(time,cost) %>% 
  slice(1L) %>% 
  pivot_longer(10:11, names_to = "Profits", values_to = "prob") %>% 
  mutate(Profits = case_when(Profits =="P" ~ " Break-even",
                             Profits =="P_50" ~ "50% profit")) %>% 
  ggplot()+
  geom_hline(yintercept = 0.5, color = "gray", size =1, linetype =2)+
  geom_line(aes((time+2004), prob, color = as.factor(cost) ),
            size = 1.2)+
  facet_wrap(~Profits)+
  scale_color_colorblind()+
  labs(y = "Probability of offseting costs",
       x = "Time",
       color = "Cost (US$)")+
  ylim(0,1)+
  theme_minimal_grid()
```


### Cypr

```{r}
box_time_mix = data.frame()
time = seq(0,10, 1)
#mix intercept
# b0_decline =-2.151
# b0_se_decline =  0.121

# tebu intercept
b0_decline =-1.518
b0_se_decline =  0.065

# b1_decline = 0.132
# b1_se_decline = 0.022

b1_decline =0.061
b1_se_decline = 0.015

n = 30000
for(i in 1:length(time)){
  
y =  rnorm(n, b0_decline,b0_se_decline) + time[i]* rnorm(n,b1_decline,b1_se_decline)  
efficacy = (1-exp(y))
a = data.frame(time = time[i],lambda=efficacy)
box_time_mix = box_time_mix %>% 
  bind_rows(a)
}


```


```{r}
mix_75 = simul_decay(data_ef =  box_time_mix, cost = 75)
mix_100 = simul_decay(data_ef = box_time_mix, cost = 100)
mix_125 = simul_decay(data_ef = box_time_mix, cost = 125)
mix = bind_rows(mix_75,mix_100, mix_125)
```


```{r}
mix %>% 
  group_by(time,cost) %>% 
  slice(1L) %>% 
  pivot_longer(10:11, names_to = "Profits", values_to = "prob") %>% 
  mutate(Profits = case_when(Profits =="P" ~ " Break-even",
                             Profits =="P_50" ~ "50% profit")) %>% 
  ggplot()+
  geom_hline(yintercept = 0.5, color = "gray", size =1, linetype =2)+
  geom_line(aes((time+2004), prob, color = as.factor(cost) ),
            size = 1.2)+
  facet_wrap(~Profits)+  
  scale_color_colorblind()+
  labs(y = "Probability of offseting costs",
       x = "Time",
       color = "Cost (US$)")+
  ylim(0,1)+
  theme_light()
```

#### Combo figura
```{r}
prob_time =  function(data, prof_class){

data %>% 
  group_by(time,cost) %>% 
  slice(1L) %>% 
  pivot_longer(10:11, names_to = "Profits", values_to = "prob") %>% 
  mutate(Profits = case_when(Profits =="P" ~ "Break-even",
                             Profits =="P_50" ~ "50% profit")) %>% 
  filter(Profits == prof_class) %>% 
  ggplot(aes((time), prob))+
    
  annotate("rect",ymin = 0, ymax =0.25, 
            xmin = -5, xmax = 15,
            fill = "#eff3ff",colour="white",
            # alpha = 0.8,
           size = 0.3)+
  annotate("rect",ymin = 0.25, ymax =0.5, 
            xmin = -5, xmax = 15,
            fill = "#bdd7e7",colour="white",
            # alpha = 0.8,
           size = 0.3)+
    annotate("rect",ymin = 0.5, ymax =0.75, 
            xmin = -5, xmax = 15,
            fill = "#6baed6",colour="white",
            # alpha = 0.8,
            size = 0.3)+
    annotate("rect",ymin = 0.75, ymax =1, 
            xmin = -5, xmax = 15,
            fill = "#2171b5", colour="white",
            # alpha = 0.8,
            size = 0.3)+
    
    
  # geom_hline(yintercept = 0.75, color = "gray", size =0.8, linetype =2)+
  geom_step(direction = "hv",size = 1.2,
            aes( color = as.factor(cost) ))+
  scale_x_continuous(breaks = seq(0,10,1))+
  # scale_color_manual(values = c("red" , "#DC143C","darkred"))+
  scale_color_manual(values = c("#fecc5c" , "#fd8d3c","#e31a1c"))+
  # scale_color_manual(values = c("#000000" , "#252525","#525252"))+
  labs(y = "Probability",
       x = "Time (years)",
       color = "Cost (US$/ha)")+
 coord_cartesian(xlim=c(0,10), ylim = c(0,1))+
  theme_light()+
    theme(#panel.grid.major = element_blank()+
          panel.grid =  element_blank())
  
  }
```
<!-- Efficacy decay 0.147 /year -->
```{r}
tebu_g1 = prob_time(tebu, prof_class ="Break-even")+
    labs(title = "High annual rate of decline"
         # subtitle = "Offset costs"
         )
tebu_g2 = prob_time(tebu, prof_class ="50% profit")+
    labs(title = "High annual rate of decline",
         subtitle = "50% profit"
         )
mix_g1 = prob_time(mix, prof_class ="Break-even")+
    labs(title = "Low annual rate of decline"
         # subtitle = "Offset costs"
         )
mix_g2 = prob_time(mix, prof_class ="50% profit")+
    labs(title = "Low annual rate of decline",
         subtitle = "50% profit"
         )
```

```{r fig.height=4, fig.width=6}
tebu_g1+mix_g1+
  plot_layout(guides = "collect")+
  plot_annotation(tag_levels = 'A')&
  theme(legend.position = "bottom",
        plot.title = element_text(size = 10))
ggsave("figs/prob_time.png", dpi = 600, height = 4, width = 7)
ggsave("figs/prob_time.pdf", dpi = 600, height = 4, width = 7)
```






